Voice Classification by Neural Networks

### 2015-05-18 paper.tex
updated authors, started abstract, minor edits

\title{Voice Classification by Neural Networks}
\author{Tony Zhang}

@@

\begin{abstract}
% TODO
% neural net to classify voice gender (age?)
% 
\end{abstract}

@@

% insert stuff about gradient descent!
Formally, we can rephrase our problem as follows: Given a set of $K$ instances $(x_k, y_k)$ and a family of functions $f(\vec{w})$ (where we write the parameters as components of vector $\vec{w}$), find the parameters that minimize some \emph{objective function} dependent on both the instances and the parameters that represents in some way the inaccuracy of the estimates $f(\vec{w})(x_k)$ of $y_k$.
For our purposes, we will minimize mean-square error, defined as
\beq
\label{eq:meansqerror}
E(\vec{w}) = \sum_k E_k(\vec{w}) = \sum_k (y_k - f(\vec{w})(x_k))^2
\eeq

@@

>>>>

\title{Voice Classification by Neural Networks}
\author{Tony Zhang, James Tsui, Maryam Bahrani}

@@

\begin{abstract}
% TODO
% neural net to classify voice gender (age?)
%

In this paper, we describe a machine learning schema for voice classification by sex. We collected %XXXXX
voice samples that we used to train an artificial neural net with a single hidden layer using stochastic gradient descent. After experimenting to determine the optimal training parameters (number of iterations, etc.), using %%10-fold cross-validation with ROC AUC as our metric to evaluate our model.
With % certain settings
we were able to produce a model that performs %stats
\end{abstract}

@@

% insert stuff about gradient descent!
Formally, we can rephrase our problem as follows: Given a set of $K$ instances $(x_k, y_k)$ and a family of functions $f(\vec{w})$,\footnote{Note that $f$ itself is a function $f:W\to X$, where $W$ is the space of all possible combinations of weights and $X$ is the space of functions from inputs---our features---to outputs---our predictions. Thus, $\vec{w}$ is a vector whose components are the parameters that determine our model.} find the parameters that minimize the inaccuracy of the estimates $f(\vec{w})(x_k)$ of $y_k$.
In particular, we are minimizing some \emph{objective function} dependent on both the instances and the parameters that quantifies that inaccuracy.
For our purposes, we will minimize mean-square error, defined as
\beq
\label{eq:meansqerror}
E(\vec{w}) = \sum_k E_k(\vec{w}) = \sum_k (y_k - f(\vec{w})(x_k))^2
\eeq

@@

\subsection{Cross Validation}

% why do we want it? +overfitting
% training/test data
%
